---
title: "Introduction to BAnOCC (Bayesian Analaysis Of Compositional Covariance)"
author: "Emma Schwager"
date: "`r Sys.Date()`"
output: 
  rmarkdown::github_document:
    toc: yes
vignette: >
  %\VignetteIndexEntry{BAnOCC (Bayesian Analysis of Compositional Covariance)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Compositional data occur in many disciplines: geology, nutrition,
economics, and ecology, to name a few. Data are compositional when
each sample is sum-constrained. For example, mineral compositions
describe a mineral in terms of the weight percentage coming from
various elements; or taxonomic compositions break down a community by
the fraction of individuals that come from a particular species. In
ecology in particular, the covariance between features is often of
interest to determine which species possible interact with each
other. However, the sum constraint of compositional data makes naive
measures inappropriate.

BAnOCC is a package for analyzing compositional covariance while
accounting for the compositional structure. Briefly, the model assumes
that the unobserved counts are log-normally distributed and then
infers the correlation matrix of the log-basis.

## How To Install
There are three options for installing BAnOCC:

* Within R
* Using compressed file from bitbucket
* Directly from bitbucket

### To install from within R 
**This is not yet available**
```{r, eval=FALSE, echo=FALSE}
source("<bioconductor URL>")
biocLite("BAnOCC")
```

### To install using a compressed file from bitbucket
**This is not yet available**

### To install directly from bitbucket
```bash
git clone https://<your-user-name>@bitbucket.org/biobakery/banocc.git
R CMD INSTALL banocc
```

## To Run
The BAnOCC package contains two things:

* `bayesStanModel`, the model BAnOCC model in the  `rstan` format
* `run_banocc`, a wrapper function for `rstan::sampling` that samples
  from the model and returns a list with various useful elements

```{r, eval=FALSE}
# This code is not run
library(banocc)
data(banocc_data)
bayesModel   <- rstan::stan_model(model_code=bayesStanModel)
bayes_output <- banocc::run_banocc(banocc_data, bayes_model=bayesModel)
```

For a full description of the possible parameters for `run_banocc`,
their default values, and the output, see

```{r, eval=FALSE} 
?run_banocc 
```